Untitled

### 2025-03-18 script/r/rbci_data.Rmd
maj vdem mean

>>>>

```{r}
#MAJ VDEM

data_final <- readRDS("data/data_rds/data_final.rds")

countries <- unique(data_final$iso)

qog%<>%
  mutate(round=case_when(between(year, 2011, 2013)~5,
                         between(year, 2014, 2015)~6,
                         between(year, 2016, 2018)~7,
                         between(year, 2019, 2021)~8,
         TRUE~NA_integer_))

qog%<>%
  group_by(iso, round)%>%
  mutate(poly_mean = ifelse(is.na(round), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
  mutate(med_corr_mean = ifelse(is.na(round), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
  ungroup()

qog %<>%
  filter(!is.na(round)) %>%
  distinct(iso, round, .keep_all = TRUE) %>%
  select(iso, round, poly_mean, med_corr_mean)

data_final %<>% left_join(qog, by=c("iso", "round"))

saveRDS(data_final, file="data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")
```
